---
output: word_document
---
#Data Importing And Cleaning
```{r echo=TRUE}
HousePrice <- read.csv("G:/Ryerson-BigData/capstone/kc_house_data.csv")
head(HousePrice)
colnames(HousePrice)
any(is.na(HousePrice$id))
any(is.na(HousePrice$date))
any(is.na(HousePrice$price))
any(is.na(HousePrice$bedrooms))
any(is.na(HousePrice$bathrooms))
any(is.na(HousePrice$sqft_living))
any(is.na(HousePrice$sqft_lot))
any(is.na(HousePrice$floors))
any(is.na(HousePrice$waterfront))
any(is.na(HousePrice$view))
any(is.na(HousePrice$condition))
any(is.na(HousePrice$grade))
any(is.na(HousePrice$sqft_above))
any(is.na(HousePrice$sqft_basement))
any(is.na(HousePrice$yr_built))
any(is.na(HousePrice$yr_renovated))
any(is.na(HousePrice$zipcode))
any(is.na(HousePrice$lat))
any(is.na(HousePrice$long))
any(is.na(HousePrice$sqft_living15))
any(is.na(HousePrice$sqft_lot15))
```





#BEDROOM ANALYSIS
```{r echo=TRUE}
hist(HousePrice$bedrooms,main = 'HousePrice',xlab = 'Bedrooms',ylab = 'No of Houses',col.main='Blue',col.axis='Blue',col.lab = 'Blue',col = 'Blue')
boxplot(HousePrice$bedrooms,main = 'HousePrice',col.main='Blue',col.axis='Blue',col.lab = 'Blue',col = 'Blue')

#*******Initial correlation = 
cor(HousePrice$bedrooms,HousePrice$price)



#*******Removing the outliers
#Since more than 7 bedrooms are very rare.Also it's the outlier for my model.
#I  have removed  the outlier data.
HousePrice<-subset(HousePrice,bedrooms>=1 & bedrooms<=7)

#*******Once we removed the outliers
#******Final Correlation =
cor(HousePrice$bedrooms,HousePrice$price)

hist(HousePrice$bedrooms,main = 'HousePrice',xlab = 'Bedrooms',ylab = 'No of Houses',col.main='Blue',col.axis='Blue',col.lab = 'Blue',col = 'Blue')
boxplot(HousePrice$bedrooms,main = 'HousePrice',xlab = 'Bedrooms',
        col.main='Blue',col.axis='Blue',col.lab = 'Blue',col = 'Blue')
 
```

#BATHROOM ANALYSIS
```{r echo=TRUE}

plot(HousePrice$price~HousePrice$bathrooms,main = 'HousePrice',xlab = 'Bathrooms',ylab = 'No of Houses',col.main='Blue',col.axis='Blue',col.lab = 'Blue',col = 'Blue')
hist(HousePrice$bathrooms,main = 'HousePrice',xlab = 'Bathrooms',ylab = 'No of Houses',col.main='Blue',col.axis='Blue',col.lab = 'Blue',col = 'Blue')
boxplot(HousePrice$bathrooms,main = 'HousePrice',xlab = 'Bathroom',col.main='Blue',col.axis='Blue',col.lab = 'Blue',col = 'Blue')
#*******Initial correlation = 
cor(HousePrice$bathrooms,HousePrice$price)


#*******Removing the outliers
#More than 4 bathrooms are very rare in this data.So I am removing it.
HousePrice<-subset(HousePrice,bathrooms>=1 & bathrooms<=4)

#*******Once we removed the outliers
plot(HousePrice$price~HousePrice$bathrooms,main = 'HousePrice',xlab = 'Bathrooms',ylab = 'No of Houses',col.main='Blue',col.axis='Blue',col.lab = 'Blue',col = 'Blue')
hist(HousePrice$bathrooms,main = 'HousePrice',xlab = 'Bathrooms',ylab = 'No of Houses',col.main='Blue',col.axis='Blue',col.lab = 'Blue',col = 'Blue')
boxplot(HousePrice$bathrooms,main = 'HousePrice',xlab = 'bathrooms',col.main='Blue',col.axis='Blue',col.lab = 'Blue',col = 'Blue')
#******Final Correlation =
cor(HousePrice$bathrooms,HousePrice$price)
```
#SQFT LIVING ANALYSIS
```{r echo=TRUE}

hist(HousePrice$sqft_living,main = 'HousePrice',xlab = 'Sqft_living',ylab = 'No of Houses',col.main='Blue',col.axis='Blue',col.lab = 'Blue',col = 'Blue')
boxplot(HousePrice$sqft_living, xlab = 'Sqft_living',col.main='Blue',col.axis='Blue',col.lab = 'Blue',col = 'Blue',main = 'HousePrice')
#*******Initial correlation = 
cor(HousePrice$sqft_living,HousePrice$price)
#

#*******Removing the outliers
HousePrice<-subset(HousePrice,sqft_living >1000 & sqft_living<=4000)

#*******Once we removed the outliers
hist(HousePrice$sqft_living,main = 'HousePrice',xlab = 'Sqft_living',ylab = 'No of Houses',col.main='Blue',col.axis='Blue',col.lab = 'Blue',col = 'Blue')
boxplot(HousePrice$sqft_living, xlab = 'Sqft_living',col.main='Blue',col.axis='Blue',col.lab = 'Blue',col = 'Blue',main = 'HousePrice')
#******Final Correlation =
cor(HousePrice$sqft_living,HousePrice$price)

```

##GRADE ANALYSIS
```{r echo=TRUE}

boxplot(HousePrice$grade,main = 'HousePrice',xlab = 'Grade',col.main='Blue',col.axis='Blue',col.lab = 'Blue',col = 'Blue')
hist(HousePrice$grade,main = 'HousePrice',xlab = 'grade',ylab = 'No of Houses',col.main='Blue',col.axis='Blue',col.lab = 'Blue',col = 'Blue')
#*******Initial correlation = 
cor(HousePrice$price,HousePrice$grade)



#*******Removing the outliers

#Most of the houses grades are between 6-10 
HousePrice<-subset(HousePrice,grade >= 6 & grade<=10)

#*******Once we removed the outliers

boxplot(HousePrice$grade,main = 'HousePrice',xlab = 'Grade',col.main='Blue',col.axis='Blue',col.lab = 'Blue',col = 'Blue')
hist(HousePrice$grade,main = 'HousePrice',xlab = 'grade',ylab = 'No of Houses'
,col.main='Blue',col.axis='Blue',col.lab = 'Blue',col = 'Blue')
#******Final Correlation = 
cor(HousePrice$price,HousePrice$grade)


```

#SQFT_ABOVE ANALYSIS
```{r echo=TRUE}

boxplot(HousePrice$sqft_above,main = 'HousePrice',xlab = 'sqft_above',col.main='Blue',col.axis='Blue',col.lab = 'Blue',col = 'Blue')
hist(HousePrice$sqft_above,main = 'HousePrice',xlab = 'sqft_above',ylab = 'No of Houses',col.main='Blue',col.axis='Blue',col.lab = 'Blue',col = 'Blue')
#*******Initial correlation =
cor(HousePrice$price,HousePrice$sqft_above)

#*******Removing the outliers
HousePrice<-subset(HousePrice,sqft_above >=500 & sqft_above<=3500)

#*******Once we removed the outliers

boxplot(HousePrice$sqft_above,main = 'HousePrice',xlab = 'sqft_above',col.main='Blue',col.axis='Blue',col.lab = 'Blue',col = 'Blue')
hist(HousePrice$sqft_above,main = 'HousePrice',xlab = 'sqft_above',ylab = 'No of Houses',col.main='Blue',col.axis='Blue',col.lab = 'Blue',col = 'Blue')
#******Final Correlation = 
cor(HousePrice$price,HousePrice$sqft_above)

```
#YR_BUILT ANALYSIS

```{r echo=TRUE}
##YR_BUILT ANALYSIS
hist(HousePrice$yr_built,main = 'HousePrice',xlab = 'yr_built',ylab = 'No of Houses',col.main='Blue',col.axis='Blue',col.lab = 'Blue',col = 'Blue')
boxplot(HousePrice$yr_built,main = 'HousePrice',xlab = 'yr_built',col.main='Blue',col.axis='Blue',col.lab = 'Blue',col = 'Blue')
#*******Initial correlation =
cor(HousePrice$price,HousePrice$yr_built)


#*******Removing the outliers
#In our data some records are too old..I just removed that data from my model.
#Because It doesn't make any sense to keep more than 100 years house in our model
HousePrice<-subset(HousePrice,yr_built>=1950& yr_built<=2015)

#*******Once we removed the outliers

hist(HousePrice$yr_built,main = 'HousePrice',xlab = 'yr_built',ylab = 'No of Houses',col.main='Blue',col.axis='Blue',col.lab = 'Blue',col = 'Blue')
boxplot(HousePrice$yr_built,main = 'HousePrice',xlab = 'yr_built',col.main='Blue',col.axis='Blue',col.lab = 'Blue',col = 'Blue')
#******Final Correlation = 
cor(HousePrice$price,HousePrice$yr_built)
```


#ZIPCODE ANALYSIS
```{r echo=TRUE}

plot(HousePrice$price~HousePrice$zipcode,main = 'HousePrice',xlab = 'zipcode',ylab = 'price',col.main='Blue',col.axis='Blue',col.lab = 'Blue',col = 'Blue')
#correlation = 
cor(HousePrice$price,HousePrice$zipcode)
```


##CONDITION aNALYSIS

```{r echo=TRUE}

hist(HousePrice$condition,main = 'HousePrice',xlab = 'condition',ylab = 'No of Houses',col.main='Blue',col.axis='Blue',col.lab = 'Blue',col = 'Blue')

#*******Removing the outliers
HousePrice<-subset(HousePrice,condition>=3& condition<=5)

#*******Once we removed the outliers
# Most of the houses are of condition 3-5

hist(HousePrice$condition,main = 'HousePrice',xlab = 'condition',ylab = 'No of Houses',col.main='Blue',col.axis='Blue',col.lab = 'Blue',col = 'Blue')
#*********correlation = 
cor(HousePrice$price,HousePrice$condition)

plot(HousePrice$price~HousePrice$condition)
```


##SQFT_BASEMENT ANALYSIS
```{r echo=TRUE}
#*******Initial correlation = 
cor(HousePrice$price,HousePrice$sqft_basement)

hist(HousePrice$sqft_basement,main = 'HousePrice',xlab = 'sqft_basment',ylab = 'No of Houses',col.main='Blue',col.axis='Blue',col.lab = 'Blue',col = 'Blue')

#*******Removing the outliers
HousePrice<-subset(HousePrice,sqft_basement >=0 & sqft_basement<=1500)

#*******Once we removed the outliers
#*************Final correlation = 
cor(HousePrice$price,HousePrice$sqft_basement)


hist(HousePrice$sqft_basement,main = 'HousePrice',xlab = 'sqft_basment',ylab = 'No of Houses',col.main='Blue',col.axis='Blue',col.lab = 'Blue',col = 'Blue')

boxplot(HousePrice$sqft_basement,main = 'HousePrice',xlab = 'sqft_basment',col.main='Blue',col.axis='Blue',col.lab = 'Blue',col = 'Blue')
```

##LAT ANALYSIS
```{r echo=TRUE}

hist(HousePrice$lat, main = 'HousePrice',xlab = 'lat',col.main='Blue',col.axis='Blue',col.lab = 'Blue',col = 'Blue')
boxplot(HousePrice$lat,main = 'HousePrice',xlab = 'lat',col.main='Blue',col.axis='Blue',col.lab = 'Blue',col = 'Blue')

#*********Initial Correlation =
cor(HousePrice$price,HousePrice$lat)

#*******Removing the outliers
HousePrice<-subset(HousePrice,lat>=47.3)

#*******Once we removed the outliers
#************Final Correlation = 
cor(HousePrice$price,HousePrice$lat)
hist(HousePrice$lat, main = 'HousePrice',xlab = 'lat',ylab = 'No of Houses',col.main='Blue',col.axis='Blue',col.lab = 'Blue',col = 'Blue')
boxplot(HousePrice$lat,main = 'HousePrice',xlab = 'lat',col.main='Blue',col.axis='Blue',col.lab = 'Blue',col = 'Blue')
```

## LONG ANALYSIS
```{r echo=TRUE}
hist(HousePrice$long,main = 'HousePrice',xlab = 'long',ylab = 'No of Houses',col.main='Blue',col.axis='Blue',col.lab = 'Blue',col = 'Blue')
#*********Initial Correlation =
cor(HousePrice$price,HousePrice$long)


#*******Removing the outliers
HousePrice<-subset(HousePrice,long>=-122.4 & long < -121.8)

#*******Once we removed the outliers
#************Final Correlation = 
cor(HousePrice$price,HousePrice$long)
hist(HousePrice$long,main = 'HousePrice',xlab = 'long',ylab = 'No of Houses',col.main='Blue',col.axis='Blue',col.lab = 'Blue',col = 'Blue')
```


## SQFT_LOT ANALYSIS
```{r echo=TRUE}

hist(HousePrice$sqft_lot,main = 'HousePrice',xlab = 'sqft_lot',ylab = 'No of Houses',col.main='Blue',col.axis='Blue',col.lab = 'Blue',col = 'Blue')
boxplot(HousePrice$sqft_lot,main = 'HousePrice',xlab = 'sqft_lot', col.main='Blue',col.axis='Blue',col.lab = 'Blue',col = 'Blue')
#*********Initial Correlation =
cor(HousePrice$price,HousePrice$sqft_lot)
#*******Removing the outliers
HousePrice<-subset(HousePrice,sqft_lot>=0 & sqft_lot<=25000)

#*******Once we removed the outliers
#************Final Correlation = 
cor(HousePrice$price,HousePrice$sqft_lot)
hist(HousePrice$sqft_lot,main = 'HousePrice',xlab = 'sqft_lot',ylab = 'No of Houses',col.main='Blue',col.axis='Blue',col.lab = 'Blue',col = 'Blue')
boxplot(HousePrice$sqft_lot,main = 'HousePrice',xlab = 'sqft_lot', col.main='Blue',col.axis='Blue',col.lab = 'Blue',col = 'Blue')
```

## FLOOR ANALYSIS
```{r echo=TRUE}

hist(HousePrice$floors,main = 'HousePrice',xlab = 'floors',ylab = 'No of Houses',col.main='Blue',col.axis='Blue',col.lab = 'Blue',col = 'Blue')
boxplot(HousePrice$floors,main = 'HousePrice',xlab = 'floors' ,col.main='Blue',col.axis='Blue',col.lab = 'Blue',col = 'Blue')
#*********Initial Correlation =
cor(HousePrice$price,HousePrice$floors)
```

## SQFT_LIVING15 ANALYSIS
```{r echo=TRUE}
hist(HousePrice$sqft_living15, main = 'HousePrice',xlab = 'sqft_living15', ylab = 'No of Houses',col.main='Blue',col.axis='Blue',col.lab = 'Blue', col = 'Blue')
boxplot(HousePrice$sqft_living15,main = 'HousePrice',xlab = 'sqft_living15', col.main='Blue',col.axis='Blue',col.lab = 'Blue',col = 'Blue')

#************Final Correlation = 
cor(HousePrice$sqft_living15,HousePrice$price )
```

##SQFT_LOT15 ANALYSIS
```{r echo=TRUE}
hist(HousePrice$sqft_lot15, main = 'HousePrice',xlab = 'sqft_lot15', ylab = 'No of Houses',col.main='Blue',col.axis='Blue',col.lab = 'Blue', col = 'Blue')
boxplot(HousePrice$sqft_lot15,main = 'HousePrice',xlab = 'sqft_lot15',col.main='Blue',col.axis='Blue',col.lab = 'Blue',col = 'Blue')
#************initial Correlation = 
cor(HousePrice$sqft_lot15,HousePrice$price)
#*******Removing the outliers
HousePrice<-subset(HousePrice,sqft_lot15>=0 & sqft_lot<=20000)

#*******Once we removed the outliers
hist(HousePrice$sqft_lot15, main = 'HousePrice',xlab = 'sqft_lot15', ylab = 'No of Houses',col.main='Blue',col.axis='Blue',col.lab = 'Blue', col = 'Blue')
boxplot(HousePrice$sqft_lot15,main = 'HousePrice',xlab = 'sqft_lot15',col.main='Blue',col.axis='Blue',col.lab = 'Blue',col = 'Blue')
#************Final Correlation = 
cor(HousePrice$sqft_lot15,HousePrice$price)
```

##Correlation among all the variables
```{r echo=TRUE}
#*******Only sqft_living & sqft_above,sqft_living & grade,sqft_living & bathrooms have good correlation between them
HousePrice$date <- NULL
cor(HousePrice)

```
# USING BORUTA for features selection and finally making model with the selected attributes
```{r echo=TRUE}
install.packages("Boruta", repos = "http://cran.us.r-project.org")
library(Boruta)
set.seed(2)
boruta.train <- Boruta(price ~., data = HousePrice , doTrace = 2,ntree = 500)
print(boruta.train)
plot(boruta.train, xlab = "", xaxt = "n")
set.seed(1)
Boruta.Short <- Boruta(price ~ ., data = HousePrice, maxRuns = 12)
```
```{r echo=TRUE}
HousePrice$date <- NULL
rn_train <- sample(nrow(HousePrice),floor(nrow(HousePrice)*0.6))
train <- HousePrice[rn_train,colnames(HousePrice)]
test <- HousePrice[-rn_train,colnames(HousePrice)]
lm <- lm(formula = price~.,data=train)
prediction <- predict(lm,newdata = test)
training_data_prediction = fitted(lm)
training_rmse = sqrt(sum((training_data_prediction-train$price)^2)/nrow(train))
testing_rmse = sqrt(sum((prediction - test$price)^2)/nrow(test))
training_rmse
testing_rmse
lm
```